Extreme heterogeneity of influenza virus infection in single cells

### 2017-09-26 paper/paper.tex
added citations

However, initiation of an actual influenza infection typically involves just a few virions infecting a few cells~\citep{varble2014influenza,mccrone2017evolutionary}. 
The dynamics of viral infection in these individual cells may not mirror bulk measurements made on many cells infected at high MOI.
Over 70 years ago, Max Delbruck showed that there was a $\sim$100-fold range in the number of progeny virions produced per cell by clonal bacteria infected with clonal bacteriophage~\citep{Delbruck:1945wo}.
Subsequent work has shown similar heterogeneity during infection with other viruses~\citep{zhu2009growth,Schulte:2014br,combe2015single,Akpinar:2016gt}, including influenza virus~\citep{Heldt:2015iz}.

@@

We took care to generate stocks of virus that were relatively ``pure'' of defective particles.
Stocks of viruses typically contain an array of biologically active viral particles, some of which are defective for replication owing to mutations or deletions in essential viral genes~\citep{von1954incomplete,huang1970defective,Brooke:2014ch,Fonville:2015cg,Lauring:2010if,Dimmock:2014dk}.
These defective particles become prevalent when a virus is grown at high MOI, where complementation permits the growth of otherwise deleterious genotypes.
To minimize the levels of defective particles, we propagated our viral stocks at low MOI for a relatively brief period of time~\citep{Xue:2016bw}.
We validated that our stocks exhibited greater purity of infectious particles than a stock propagated at high MOI by verifying that they had a higher ratio of infectious particles to virion RNA (Figure~\ref{fig:viruspopulations}A) and to particles capable of inducing expression of a single viral protein (Figure~\ref{fig:viruspopulations}B).
In addition, viral stocks with many defective particles are more immunostimulatory~\citep{Tapia:2013kf,Lopez:2014en}.
We confirmed that our viral stocks induced less interferon than a stock propagated at higher MOI (Figure~\ref{fig:viruspopulations}C).

>>>>

However, initiation of an actual influenza infection typically involves just a few virions infecting a few cells~\citep{varble2014influenza,poon2016quantifying,leonard2017transmission,mccrone2017evolutionary}. 
The dynamics of viral infection in these individual cells may not mirror bulk measurements made on many cells infected at high MOI.
Over 70 years ago, Max Delbruck showed that there was a $\sim$100-fold range in the number of progeny virions produced per cell by clonal bacteria infected with clonal bacteriophage~\citep{Delbruck:1945wo}.
Subsequent work has shown similar heterogeneity during infection with other viruses~\citep{zhu2009growth,Schulte:2014br,combe2015single,Akpinar:2016gt}, including influenza virus~\citep{Heldt:2015iz}.

@@

We took care to generate stocks of virus that were relatively ``pure'' of defective particles.
Stocks of viruses typically contain an array of biologically active viral particles, some of which are defective for replication owing to mutations or deletions in essential viral genes~\citep{von1954incomplete,huang1970defective,Brooke:2014ch,Fonville:2015cg,Lauring:2010if,Dimmock:2014dk,saira2013sequence}.
These defective particles become prevalent when a virus is grown at high MOI, where complementation permits the growth of otherwise deleterious genotypes.
To minimize the levels of defective particles, we propagated our viral stocks at low MOI for a relatively brief period of time~\citep{Xue:2016bw}.
We validated that our stocks exhibited greater purity of infectious particles than a stock propagated at high MOI by verifying that they had a higher ratio of infectious particles to virion RNA (Figure~\ref{fig:viruspopulations}A) and to particles capable of inducing expression of a single viral protein (Figure~\ref{fig:viruspopulations}B).
In addition, viral stocks with many defective particles are more immunostimulatory~\citep{Tapia:2013kf,Lopez:2014en}.
We confirmed that our viral stocks induced less interferon than a stock propagated at higher MOI (Figure~\ref{fig:viruspopulations}C).
